PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-07-10 txt/manuscript_short.tex

Without loss of generality\footnote{Explaining why we can consider only discrimination scheme
between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper. See
\cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between
single qubit measurements $\PP_\Id$, performed in the computational Z-basis, and an alternative
measurement $\PP_U$ performed in the basis $U$. Note, however, that the discrimination scheme
described below can work regardless of dimensionality of the system, see
\cite{puchala2018strategies} for details.

The discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the
measurements, either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
outcome $i$, we choose another measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
obtaining the outcome $j$. Finally, if $j=0$, we say that the performed measurement is
$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
probability distribution. In PyQBench, we assume that the experiment is repeated the same number of
times for both $\PP_U$ and $\PP_\Id$.

>>>>

Without loss of generality\footnote{Explaining why we can consider only discrimination scheme
between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper. See
\cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between
single qubit measurements $\PP_\Id$, performed in the computational Z-basis, and an alternative
measurement $\PP_U$ performed in the basis $U$. 
The discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the
measurements, either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
outcome $i$, we choose another binary measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
obtaining the outcome $j$. Finally, if $j=0$, we say that the performed measurement is
$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$.

Note, however, that the discrimination scheme
described above can work regardless of dimensionality of the unitary $U$ with such a difference that the size of auxiliary system can be larger than the qubit. This size depends on the input state which was taken, explicitly on the Schmidt rank of the optimal input state. However, for most discrimination schemes, the  Schmidt rank equals at most two, hence the size of auxiliary system remains qubit, see \cite{puchala2018strategies} for details. It is also worth mentioning that despite of the size of auxiliary system, the final measurement $\PP_{V_i}$ is always binary.

Naturally, we need to repeat the
same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
probability distribution. In PyQBench, we assume that the experiment is repeated the same number of
times for both $\PP_U$ and $\PP_\Id$.
